---
title: "Final Project Rough Draft"
author: "Adharsh Vanchinathan"
date: "Due 3/13/2020"
output:
  html_document: default
---

`Restate the Problem Statement`
Problem Statement: Is the Internet and the ways to access it detrimental to human wellbeing?

Could internet access be a path to more educated, economically powerful country?

“Using the key internet access indicators, we are able to contrast each country’s economic and educational data with their internet access data, providing clear patterns by plotting the data.”


# The Plan

## Introduction
- Provide Engaging and Informative intro to Problem Statement

- Explain why this problem, data and methods used

- Discuss your approach and analysis and why it addresses issue

- How analysis helps reader
-World

  - internet availability % over time
  - Mobile Phone user % over time
  - Tech Market Share over time
  - Social Media membership over time(color by social media app)
  - Population
  - Median Income
  - Digital Media usage over time(USA Data)

-Countries (over time)
  - internet availability (number)
  - internet availability (%)
  - Mobile Phone user % 
  - GDP
  - GDP Per Capita
  - Median Income

Comparison: EU Rivals
- France
- Germany


Comparison: Countries with similar populations
- South Korea
- Myanmar


Comparison: Countries with similar internet Users
- Canada
- Thailand

Comparison: Countries with similar GDP/Capita

Make conclusions based on comparisons
Summary

`EDIT`
  The Internet has been a juggernaut of social and cultural change, bringing people together and providing forums and spaces to voice their opinions, display their creative efforts, and even conduct business. However, many of us with access to it take the internet and its effects for granted. Could internet access be a path to more educated, economically powerful country? The effects of internet access and how the access inequality affects countries as a whole has not been extensively studied, and may provide insight into why internet infrastructure is a necessary investment for a 21st century government. By collecting data on the numbers of non-cellular internet users, % of population that are mobile internet users, % of population who are internet users, and comparing it to their population, GDP, GDP per Capita, and national average learning outcomes, we will attempt to shed more light on the potential of internet access as a key indicator for future success. Using the key internet access indicators, we are able to contrast each country's economic and educational data with their internet access data, providing clear patterns by plotting the data.

```{r setup}
knitr::opts_chunk$set(eval = T)
# Change the scipen option to 999 to prevent Scientific Notation
options(scipen = 999)
# The tidyverse package is loaded in to allow for ease of data manipulation
# And the start up message is suppressed 
suppressPackageStartupMessages(library(tidyverse))

```
Tech data citation:
`Finish Citation blurbs`

- Internet users/availability

 The entity, year and number of internet users was selected to show the data that is
important to exemplify the number of internet users.

Roser, Max, et al. “Internet, how many internet users does each country have/number of internet users
by country.” Our World in Data, 14 July 2015, ourworldindata.org/internet.

- Smartphone users

 The mobile cellular subscriptions per 100 people data was selected by entity, year
and mobile subscriptions and filtered by the country. This data is important because it shows the amount of
mobile subscriptions.

Roser, Max, et al. “Internet, Mobile Phone Users/Mobile cellular subscriptions per 100 people.” Our
World in Data, 14 July 2015, ourworldindata.org/internet.

- Digital media usage


Roser, Max, et al. “Internet, Social media/Daily hours spent with digital media.” Our World in Data, 14
July 2015, ourworldindata.org/internet.

- Percent of population internet usage
Roser, Max, et al. “Internet, how many internet users does each country have/share of population using
the internet.” Our World in Data, 14 July 2015, ourworldindata.org/internet.

- Users by social media platform:
Roser, Max, et al. “Internet, The Rise of Social Media/Number of people using social media
platforms.” Our World in Data, 14 July 2015, ourworldindata.org/internet.
Population data citation:
Datopian. “Population, Total.” DataHub, datahub.io/world-bank/sp.pop.totl.
Economics and Education data:

- GDP
Datopian. “Country, Regional and World GDP (Gross Domestic Product).” DataHub,
datahub.io/core/gdp.

- National average learning outcome
Roser, Max, and Esteban Ortiz-Ospina. “Global Education.” Our World in Data, 31 Aug. 2016,
ourworldindata.org/global-education.


## Data Prep:
`Write out details for each data import`
`Use head() to show each data set`
`Provide summary of variables`

- Source is cited and Hyperlinked
- Source Data is thoroughly explained 
  - Who collected it
  - Why it was Collected
  - When it was collected
  - Is there anything wrong or weird about this Data?
- Data Import is logical and explained
- Show final data set(s) in the most condensed form
- Provide a summary for variables of interest

- Internet users/availability
```{r net_user_load}
net_users_raw <- as.tibble(read.csv(file = "Data/number-of-internet-users-by-country.csv")) %>% rename(Num_Net_Users = Number.of.internet.users..users.)
net_users_wld <- net_users_raw %>% filter(Entity == "World") %>% select(Entity,Year,Num_Net_Users) %>% arrange(Year)
net_users_wld


```

- Smartphone users
```{r smartphone_load}
mobile_use_raw <- as.tibble(read.csv(file = "Data/mobile-cellular-subscriptions-per-100-people.csv")) %>% rename(Mobile_Per_100 = Mobile.cellular.subscriptions..per.100.people...per.100.people.) %>% filter(Year > 1989)
mobile_use_wld <- mobile_use_raw %>% filter(Entity == "World") %>% select(Entity, Year, Mobile_Per_100 ) %>% arrange(Year)

```

- Digital media usage
```{r social_media_load}
US_DM_use <- as.tibble(read.csv(file = "Data/daily-hours-spent-with-digital-media-per-adult-user.csv"))
US_DM_use
```

- % of pop internet usage
```{r net_percent_load}
net_per_raw <- as.tibble(read.csv(file = "Data/share-of-individuals-using-the-internet.csv")) %>% rename(Percent_Internet =Individuals.using.the.Internet....of.population.....of.population.)
net_per_wld <- net_per_raw %>% filter(Entity == "World") %>% select(Entity,Year,Percent_Internet) %>% arrange(Year)
net_per_raw %>% filter(Entity == "Russia")

```

- Users by Social Media Platform
```{r sm_user_load}
sm_user_raw <- as.tibble(read.csv(file = "Data/users-by-social-media-platform.csv"))
sm_user <- sm_user_raw %>% rename(Monthly_Users = Monthly.active.users..Statista.and.TNW..2019....MAU.) %>% filter(Entity == "Facebook"| Entity == "Instagram"|Entity == "Reddit"|Entity == "YouTube")
sm_user
```
## Population Data

```{r world_pop_load}
pop_raw <- as.tibble(read.csv(file = "Data/population.csv")) %>% rename(pop = Value) %>% filter(Year > 1989)
wld_pop <- pop_raw %>% filter(Country.Name == "World")
#wld_pop
pop_raw 



```

## Economics and Education

- GDP
```{r GDP_load}
GDP <-read.csv(file = "Data/gdp_csv.csv")%>% rename(GDP = Value) %>% filter(Year > 1989)
GDP_wld<- GDP %>% filter(Country.Name == "World")
GDP %>% filter(Country.Code == "RUS")

```
- Average Learning Outcome(ALO)
```{r ALO_load}
ALO_tbl <- as.tbl(read.csv(file = "Data/average-harmonized-learning-outcome-scores.csv")) %>% filter(Code != "") %>% rename(ALO = Average.harmonised.learning.outcome.score..Altinok..Angrist..and.Patrinos..2018......score..)

ALO_tbl<- ALO_tbl %>% filter(Year%%5 == 0)
ALO_tbl
```



## Data Analysis:
`Make ALO Graphs increments of 5`
`Properly format and organize description paragraphs`
`Properly label Plots`
`Add GDP per capita vs mobile % Plot`

- Uncover new info that isn't apparent
- Display findings in tables or plots
- Use Graphs to illustrate your primary point
- Use tables to compare and highlight important differences
- Analysis should be thorough and concise
- Easy to Follow



# World Data

## Create DF with World Data (wld_data)

Using the data we just gathered and discussed, we must first show the trends of the data as a whole, using World data to determine how the countries we explore compare to the global average.
First we consolidate the disparate dataframes into one `wld_data` Dataframe.


```{r wld_data_init}
wld_data <- full_join(wld_pop,net_users_wld,by = "Year") %>% left_join(mobile_use_wld, by = "Year") %>% left_join(net_per_wld, by = "Year") %>% left_join(GDP_wld, by = "Year") %>% select(Entity = Country.Name.y, Year, pop, Num_Net_Users, Mobile_Per_100, Percent_Internet, GDP) %>% mutate(mobile_pop = (Mobile_Per_100*.01)*pop) %>% mutate(GDP_Capita = GDP/pop)
wld_data

```

First, lets graph the world population, number of mobile subscriptions, and the number of broadband/wi-fi internet users. This graph clearly illustrates how pervasive technology is in our modern lives. 
# Plotting
## Population, Internet users, mobile users

```{r}
ggplot(wld_data)+
  geom_line(aes(Year,pop),color = "Red")+
  geom_line(aes(Year,Num_Net_Users), color = "Green")+
  geom_smooth(aes(Year,mobile_pop), color = "Blue")+
  scale_x_continuous(limits = c(1990,2016), breaks = c(1990,1995,2000,2005,2010,2015))
# Need to facet or Label each graph
# Make it Pretty
  
```
Now we graph the GDP per Capita to provide a mean baseline to judge our selected countries against to see if they above or below the World average.
## GDP
```{r}
ggplot(wld_data)+
  geom_line(aes(Year,GDP_Capita))+
  labs(title = "World GDP over time", x = "Time(Years)", y = "Nominal GDP per Capita (In current USD)")
```

Then we analyse the world Mobile User and Internet users by percent(%). This is again just a baseline to compare the our selected countries.

## Internet and Mobile Users (%)

```{r}
mob_100 <- mobile_use_wld %>% select(Year, val = Mobile_Per_100)
per_int <- net_per_wld %>% select(Year,val = Percent_Internet)
ggplot(NULL, aes(Year, val)) + 
  geom_col(aes(fill = "Monthly Mobile Users"), data = mob_100, alpha = 0.5,position = "dodge") +  geom_col(aes(fill = "Percent of Population with wired internet access"), data = per_int, alpha = 0.5,position = "dodge")+
  scale_y_continuous(limits = c(0,100))
```
With just Social Media being a major contributor to the rapid assimilation of the internet, it is paramount to show how just over barely a decade, industry titans like Facebook and Youtube have over 1.5 billion monthly users.

```{r}
ggplot(sm_user)+
  geom_line(aes(Year,Monthly_Users))+
  facet_wrap(vars(Entity))
```

## Digital Media Consumption in the US

```{r}
#Digital Media Consumption in US graph(Phone,Laptop,Other)
```


# Country Comparison
For each Country:
Pop
Net_users
Mobile_use_%
net_%
gdp_%


First, lets compare the two largest rivals in the EU.


First we create FR and DE dataframes to combine and create a World-US-Russia dataframe to make comparisons
```{r FR-data}
FR_data <- left_join(pop_raw %>% filter(Country.Code == "FRA"),net_users_raw %>% filter(Code == "FRA"),by = "Year") %>% left_join(mobile_use_raw %>% filter(Code == "FRA"), by = "Year") %>% left_join(net_per_raw %>% filter(Code == "FRA")) %>% left_join(GDP) %>% filter(Country.Code == "FRA")%>% left_join(ALO_tbl) %>% filter(Code == "FRA") %>% select(Entity,Year,pop,Num_Net_Users,Mobile_Per_100,Percent_Internet,GDP,ALO) %>% mutate(mobile_pop = (Mobile_Per_100*.01)*pop)
FR_data
```

```{r DE-data}

DE_data <- left_join(pop_raw %>% filter(Country.Code == "DEU"),net_users_raw %>% filter(Code == "DEU"),by = "Year") %>% left_join(mobile_use_raw %>% filter(Code == "DEU"), by = "Year") %>% left_join(net_per_raw %>% filter(Code == "DEU")) %>% left_join(GDP) %>% filter(Country.Code == "DEU") %>% left_join(ALO_tbl) %>% filter(Code == "DEU") %>% select(Entity = Country.Name,Year,pop,Num_Net_Users,Mobile_Per_100,Percent_Internet,GDP,ALO) %>% mutate(mobile_pop = (Mobile_Per_100*.01)*pop)
DE_data

```


```{r World-France-Germany}

WFD_data <- bind_rows(wld_data,FR_data,DE_data) %>% mutate(GDP_Capita = GDP/pop)
WFD_data
```

First we compare the Populations of France and Germany

Two countries that have been intertwined since their inceptions. Both economic and cultural powerhouses of Western Europe, this comparison will help demonstrate the approach to examine the data critically in the lens of the question.
```{r pop_1}
ggplot(WFD_data %>% filter(Entity != "World"))+
  geom_col(aes(Year,pop,color = Entity), position = "dodge")
```
Note that Germany has had a consistently higher population despite the dip in the early 2010's.  

Now the internet access graphs for both countries
```{r Internet_1}
ggplot(WFD_data)+
  geom_line(aes(Year,Percent_Internet, color = Entity))
ggplot(WFD_data)+
  geom_line(aes(Year,Mobile_Per_100, color = Entity))

```
Both these countries have wildly better internet access than the world average, and it will not be hard to see why. As hubs of tourism, industry, manufacturing, design, and commerce, these countries need to be equipped with robust and powerful internet infrastructure and access.


GDP per Capita

```{r GDP_1}
ggplot(WFD_data)+ #%>% filter(Entity != "World"))+
  geom_line(aes(Year,GDP_Capita, color = Entity))

```
Both these countries also have very similar GDPs, especially over time. While Germany edges out France by the end of the data set, Both these countries are incredibly wealthy compared to the World GDP(in blue).
```{r}
ggplot(WFD_data %>% filter(Entity != "World"))+
  geom_col(aes(Year,ALO, color = Entity), position = "dodge")
  
```
Starting with the French in a slight advantage, over the years the scene changes and Germany is on top, but still marginally. Both these countries are quite similar in terms of their education standards, economic output, and internet access. While Germany is better by a hair, both are star examples of a developed, modern country.

Moving onto South Korea and Myanmar, both these countries are located in Asia and have similar populations at the end of the dataset(2016). By comparing their internet access, economies and education, we can start to see the association between internet access and our chosen indicators.


We import South Korea data into an independent dataframe
```{r SK_data}
SK_data <- left_join(pop_raw %>% filter(Country.Code == "KOR"),net_users_raw %>% filter(Code == "KOR"),by = "Year") %>% left_join(mobile_use_raw %>% filter(Code == "KOR"), by = "Year") %>% left_join(net_per_raw %>% filter(Code == "KOR")) %>% left_join(GDP) %>% filter(Country.Code == "KOR")%>% left_join(ALO_tbl) %>% filter(Code == "KOR") %>%  select(Entity,Year,pop,Num_Net_Users,Mobile_Per_100,Percent_Internet,GDP,ALO) %>% mutate(mobile_pop = (Mobile_Per_100*.01)*pop)
SK_data


```

We import Myanmar data into independent dataframe
```{r MM_data}
MM_data <- left_join(pop_raw %>% filter(Country.Code == "MMR"),net_users_raw %>% filter(Code == "MMR"),by = "Year") %>% left_join(mobile_use_raw %>% filter(Code == "MMR"), by = "Year") %>% left_join(net_per_raw %>% filter(Code == "MMR")) %>% left_join(GDP) %>% filter(Country.Code == "MMR") %>% left_join(ALO_tbl) %>% filter(Code == "MMR") %>% select(Entity = Country.Name,Year,pop,Num_Net_Users,Mobile_Per_100,Percent_Internet,GDP,ALO) %>% mutate(mobile_pop = (Mobile_Per_100*.01)*pop) %>% filter(Year >=1999)
MM_data

```

We combine the world, Korea and Myanmar data into WKM_data
```{r World-SK-Myanmar}

WKM_data <- bind_rows(wld_data ,SK_data,MM_data) %>% 
  filter(Year >= 2000)%>% mutate(GDP_Capita = GDP/pop)
WKM_data
```


First we plot their populations
```{r pop_2}
ggplot(WKM_data %>% filter(Entity != "World"))+
  geom_col(aes(Year,pop,color = Entity),position = "dodge")
```

We can see that both these countries have had nearly identical population numbers since data is available (Myanmar only has data from 2000 onwards). Now to compare their internet coverage

```{r Internet_2}
ggplot(WKM_data)+
  geom_line(aes(Year,Percent_Internet, color = Entity))
ggplot(WKM_data)+
  geom_line(aes(Year,Mobile_Per_100, color = Entity))

```
Myanmar functionally did not have any internet capacity until 2010 at the earliest. Comparing this with South Korea, the numbers increased the most drastically even before the turn of the century, shooting up from 15% in 1997 to nearly 50% in 1999. This early adoption paid dividends compared to Myanmar's measly 25% in 2016. But in terms of mobile user percentages, Myanmar has increased its numbers drastically from 7% in 2012 to nearly 75& in 2016, showing a trend that countries that don't invest in a wired internet system often opt for mobile. One interesting observation is that Myanmar's mobile infrastructure grew rapidly from 2012 onwards. This may be because Mobile Infrastructure and mobile internet as a whole is cheaper for both consumers and providers.

```{r GDP_2}
ggplot(SK_data)+
  geom_point(aes(Year,GDP/pop))
ggplot(MM_data)+
  geom_point(aes(Year,GDP/pop), color = "Red")
ggplot(WKM_data)+
  geom_point(aes(Year,GDP_Capita, color = Entity))

```

Graphing the GDP per Capita, it is easy to see the wealth disparity between these two nations. South Korea's data doesn't prove that internet access leads to greater economic power. However, Myanmar's data clearly shows that around 2010, with the rise of internet and especially mobile users, their GDP per capita accelerated upward and has maintained around $1250 since then. The increased access of the internet seems to have stabilised this country's economy. But regardless of their relative success, their GDP grwoth barely displays on the graph and South Korea clearly outshines it in terms of economy as well.
```{r}
ggplot(NULL, aes(Year,ALO))+
  geom_point(data = DE_data, color = "Blue")+
  geom_point(data = SK_data)
  
```
Myanmar does not have any ALO information, this may be due to the precarious governmental organization there, but South Korea has consistently scored higher than Germany , so it would suffice it to say South Korea is far more educated than Myanmar based on the previous analyses. This shows that not only does internet access beget wealth, but wealth begets internet access.

Finally, Two countries with similar populations with access to Internet. Lets assess Canada and Thailand.

We load in each country into their own dataframes and combine them into WCT_data
```{r CA_data}
CA_data <- left_join(pop_raw %>% filter(Country.Code == "CAN"),net_users_raw %>% filter(Code == "CAN"),by = "Year") %>% left_join(mobile_use_raw %>% filter(Code == "CAN"), by = "Year") %>% left_join(net_per_raw %>% filter(Code == "CAN")) %>% left_join(GDP) %>% filter(Country.Code == "CAN")%>% left_join(ALO_tbl) %>% filter(Code == "CAN") %>% select(Entity,Year,pop,Num_Net_Users,Mobile_Per_100,Percent_Internet,GDP,ALO) %>% mutate(mobile_pop = (Mobile_Per_100*.01)*pop) 
CA_data

```
```{r TL_data}
TL_data <- left_join(pop_raw %>% filter(Country.Code == "THA"),net_users_raw %>% filter(Code == "THA"),by = "Year") %>% left_join(mobile_use_raw %>% filter(Code == "THA"), by = "Year") %>% left_join(net_per_raw %>% filter(Code == "THA")) %>% left_join(GDP) %>% filter(Country.Code == "THA") %>% left_join(ALO_tbl) %>% filter(Code == "THA")%>% select(Entity = Country.Name,Year,pop,Num_Net_Users,Mobile_Per_100,Percent_Internet,GDP,ALO) %>% mutate(mobile_pop = (Mobile_Per_100*.01)*pop) 
TL_data

```
```{r World-Canada-Thailand}

WCT_data <- bind_rows(wld_data,CA_data,TL_data) %>% mutate(GDP_Capita = GDP/pop)
WCT_data
```

First we take a look at their populations.
```{r pop_3}
ggplot(WCT_data %>% filter(Entity != "World"))+
  geom_col(aes(Year,pop,color = Entity),position = "dodge")
```
While both countries have similar growth, Thailand simply has a much larger population.
```{r Internet_3}
ggplot(WCT_data %>% filter(Entity != "World"))+
  geom_line(aes(Year,Num_Net_Users, color = Entity))
ggplot(WCT_data)+
  geom_line(aes(Year,Percent_Internet, color = Entity))
ggplot(WCT_data)+
  geom_line(aes(Year,Mobile_Per_100, color = Entity))


```
While both Canada and Thailand has similar raw numbers of internet users, Thailand's larger populace means that less of Thailand has access to reliable wired networks. Much like Myanmar, There is a much larger spike in mobile access, far surpassing Canada. This may be due to the earlier adoption of internet by the Canadians, leading to a lower demand for mobile internet.

```{r GDP_3}
ggplot(WCT_data %>% filter(Entity !="World"))+
  geom_point(aes(Year,GDP_Capita, color = Entity))

```
This GDP per Capita graph quite clearly illustrates the magnitude of separation between these countries, economically speaking. Canada is a global power, with the adequate funding and infrastructure to adopt internet early on, from the mid 90's. 

```{r ALO_3}
ggplot(WCT_data %>% filter(Entity != "World"))+
  geom_point(aes(Year,ALO, color = Entity))
```
The Thai ALO scores plummet from the year 2000. This may be due to the new distraction of the internet, or maybe there was political or social upheaval. But Canada, as a stable, rich nation, maintains or improves their performance.


  


- Mobile internet is more populat with poor countries

## Summary/Conclusion
`Make bullet points into cohesive paragraph`

- Problem Statement
  - How does internet access affect a country's economics and education

- How it was addressed
  - A set of 6 countries are examined based on internet availability, GDP, and ALO

- Insight given by analysis
  - Showed that poorer countries opt for mobile instead of broadband, Rich countries often invested early into internet access, Countries with similar economic and educational data tend to have similar internet access.

- Implications of findings
  - While it cant be outright determined if internet access has a positive effect on a country, It would seem that countries that invested early into broadband fare better economically and intellectually.

- Discuss limitations of findings
  - There is some data missing from a few dataframes,
We could use more economic and educational indicators(i.e. Eco: CPI, Inflation, Unemployment)(i.e. Edu: Standardized Test Scores, graduation rates) as well as internet *speed* data.



