---
title: "Homework 4"
author: "Adharsh Vanchinathan"
date: "Due 3/13/2020"
output:
  html_document: default
---


Problem Statement: Is the Internet and the ways to access it detrimental to human wellbeing?

```{r setup}
knitr::opts_chunk$set(eval = T)

suppressPackageStartupMessages(library(tidyverse))

```
Data:

- Internet users/availability
```{r net_user_load}
net_users <- read.csv(file = "Data/number-of-internet-users-by-country.csv")
```


- Smartphone users
```{r smartphone_load}
mobile_use <- read.csv(file = "Data/mobile-cellular-subscriptions-per-100-people.csv")
```

- Digital media usage
```{r social_media_load}
DM_use <- read.csv(file = "Data/daily-hours-spent-with-digital-media-per-adult-user.csv")
```

- % of pop internet usage
```{r net_percent_load}
net_per <- read.csv(file = "Data/share-of-individuals-using-the-internet.csv")

```


- Tech market share

- Global Population Data

- Economic data
  - GDP
  - Stock Market
  - etc.

- Health Data
  - Physical Activity
  - Obesity 
  - Heart Issues
  
0. Introduction

1. Gather and Display Tech Data
  
  - Import data from .csv files
  - Clean up the Data and filter out unused data
  - Display Graphs
  - Show Data
  - Make data % of world pop and apply a regression to project the future

2. Relating Tech Data

  - Age group internet usage over time
  - Help establish the different types of users
  - Provide a reason to care about the Data

3. Relating Health Data

  - Provide health data for each age group introduced in Part 2
  - Correlate health stats with technology usage per age group

4. Relating Economic Data
  - Provide correlation of technological advancement to Economic prosperity
  - Compare market share data over time

5. Low-internet vs high-internet Country comparison
  - Pick 2 countries with similar populations in similar regions of the world
  - Compare quality of life
  - Compare economic status over time
  - Make conclusions based on this information
  
6. Projection of Technology

  - VR/AR projections
  - 5G projections 
  
6. Summary/Conclusion








