---
title: "Homework 4"
author: "Adharsh Vanchinathan"
date: "Due 3/13/2020"
output:
  html_document: default
---


Problem Statement: Is the Internet and the ways to access it detrimental to human wellbeing?

```{r setup}
knitr::opts_chunk$set(eval = T)
options(scipen = 999)
suppressPackageStartupMessages(library(tidyverse))

```
Data:

- Internet users/availability
```{r net_user_load}
net_users_raw <- as.tibble(read.csv(file = "Data/number-of-internet-users-by-country.csv"))
net_users <- net_users_raw %>% filter(Entity == "World") %>% select(Entity,Year,Num_Net_Users = Number.of.internet.users..users.) %>% arrange(Year)
net_users
```


- Smartphone users
```{r smartphone_load}
mobile_use_raw <- as.tibble(read.csv(file = "Data/mobile-cellular-subscriptions-per-100-people.csv"))
mobile_use <- mobile_use_raw %>% filter(Entity == "World",Year > 1989) %>% select(Entity, Year, Mobile_Per_100 = Mobile.cellular.subscriptions..per.100.people...per.100.people.) %>% arrange(Year)
mobile_use
```

- Digital media usage
```{r social_media_load}
US_DM_use_raw <- as.tibble(read.csv(file = "Data/daily-hours-spent-with-digital-media-per-adult-user.csv"))
US_DM_use <- US_DM_use_raw 
US_DM_use
```

- % of pop internet usage
```{r net_percent_load}
net_per_raw <- as.tibble(read.csv(file = "Data/share-of-individuals-using-the-internet.csv"))
net_per <- net_per_raw %>% filter(Entity == "World") %>% select(Entity,Year,Percent_Internet =Individuals.using.the.Internet....of.population.....of.population.) %>% arrange(Year)
net_per

```

- Users by Social Media Platform
```{r sm_user_load}
sm_user_raw <- as.tibble(read.csv(file = "Data/users-by-social-media-platform.csv"))
sm_user <- sm_user_raw %>% group_by(Year) %>% summarise(sm_sum = sum(Monthly.active.users..Statista.and.TNW..2019....MAU.))
# Find the cumulative amount of users per year
sm_user

```





- Global Population Data
```{r world_pop_load}

world_pop_raw <- as.tibble(read.csv(file = "Data/population.csv"))
world_pop <- world_pop_raw %>% filter(Entity == "World") %>% select(Entity,Year,Pop = Population) %>% slice(122:151)
world_pop


```


- Economic data
  - GDP
  - Stock Market
  - Tech market share
  - etc.

- Health Data
  - Physical Activity
  - Diabetes25
  - Obesity
  - Heart Issues
  
0. Introduction

1. Gather and Display Tech Data
  
  - Import data from .csv files
```{r}
tech_data <- # join together 
```


  - Clean up the Data and filter out unused data

```{r net_users_graph}
ggplot(net_users)+
  geom_point(mapping = aes(x = Year,y = Num_Net_Users))
```

```{r smartphone_user_graph}
ggplot(mobile_use)+
  geom_point(mapping = aes(x = Year, y = Mobile_Per_100))
```
```{r internet_per_graph}
ggplot(net_per)+
  geom_point(mapping = aes(x = Year,y = Percent_Internet))

```


  - Display Graphs
```{r}
ggplot(sm_user)+
  geom_point(mapping = aes(x = Year, y = sm_sum))

```

  - Create a graph that plots all the tech data and population data
  - Show Data
  - Make data % of world pop and apply a regression to project the future

2. Relating Tech Data

  - Age group internet usage over time
  - Help establish the different types of users
  - Provide a reason to care about the Data

3. Relating Health Data

  - Provide health data for each age group introduced in Part 2
  - Correlate health stats with technology usage per age group

4. Relating Economic Data
  - Provide correlation of technological advancement to Economic prosperity
  - Compare market share data over time

5. Low-internet vs high-internet Country comparison
  - Pick 2 countries with similar populations in similar regions of the world
  - Compare quality of life
  - Compare economic status over time
  - Make conclusions based on this information
  
6. Projection of Technology

  - VR/AR projections
  - 5G projections 
  
6. Summary/Conclusion








